---
title: "Untitled"
author: "Hanadi Fahrat, Timothy Lee, Matthew Brown, Diana Paicu, Aya Salka"
date: "December 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)



# Library Used

library(tidyverse)
library(dplyr)
library(ggplot2)
library(haven)
#library(randomForest)
```

```{r}
Data_Household<-read_por("~/STAT305/National Health Interview Survey (2)/National Health Interview Survey/DS0001/04349-0001-Data.por")

Data_Family <- read_por("~/STAT305/National Health Interview Survey (2)/National Health Interview Survey/DS0002/04349-0002-Data.por")

Data_Person <- read_por("~/STAT305/National Health Interview Survey (2)/National Health Interview Survey/DS0003/04349-0003-Data.por")

Data_Sample_Adult <- read_por("~/STAT305/National Health Interview Survey (2)/National Health Interview Survey/DS0004/04349-0004-Data.por")
```



###Data_Household  
#### Rename the variables and create a new data frame "Data_Household_1"

```{r} 
# Data_Household  

# Rename the Variables


HHX<-Data_Household$HHX

Region<-Data_Household$REGION



```


```{r}

# Create a new dataframe

Data_Household_1<-data.frame(HHX,Region)
```


###Data_Family
####Rename the variables, create a new dataframe Data_Family_1


```{r}
# Data_Family

# Rename the Variables

HHX1<- Data_Family$HHX

Family_no<-Data_Family$FMX

Gov_Assist<-Data_Family$FFDSTYN

```


```{r}
# Create a new dataframe

Data_Family_1<-data.frame(HHX1, Family_no,Gov_Assist)
```


###Join the  2 data sets Data_Household_1 and Data_Family_1 and name the new dataframe "Data_join_1".


```{r}
Data_join_1<-inner_join( Data_Family_1 , Data_Household_1, by = c("HHX1" ="HHX"), Region)
#Data_join_1
```


##Data_Person

#### We need to rename the variables, re-level Salary, Education, and Limitation, create new data frame, create new variable Poverty_Guid , and finally join the newly formed data with the previous one by HHX as identifier.

```{r}

# Data_Person

# Rename the Variables

HHX2<-Data_Person$HHX

Person_no<- Data_Person$FPX

Family_no_1<-Data_Person$FMX

Sample_Adult<-Data_Person$ASTATFLG

Education<-Data_Person$EDUC1

Sex<-Data_Person$SEX

Age<-Data_Person$AGE_P

Marital_Status<-Data_Person$R_MARITL 

US_Citizen<-Data_Person$CITIZENP

Employed <-Data_Person$WRKLYR1

Salary<-Data_Person$ERNYR_P 

Have_Applied_SSI<-Data_Person$PSSAPL 

WorkersCompens_Unemploy<-Data_Person$PINCOT 

Child_Support<-Data_Person$PCHLDSP 

Stock_Property_Income<-Data_Person$PDIVD 

Interest_Savings<-Data_Person$PINTRSTR 

Receive_SSI<- Data_Person$PSSI 

Retirement_Pension<-Data_Person$POPENS 

Other_Disability_Pension<-Data_Person$PPENS 

Receive_SS<-Data_Person$PSSRR

limitation<-Data_Person$LACHRONR



```



```{r}
# Create a new data set and name it Data_Person_1

Data_Person_1<-data.frame(HHX2,Family_no_1,Person_no,Sample_Adult,Sex,Age,Marital_Status,Education,US_Citizen,Employed, Salary ,Have_Applied_SSI, WorkersCompens_Unemploy, Child_Support, Stock_Property_Income,Interest_Savings, Receive_SSI, Retirement_Pension,Other_Disability_Pension,
Receive_SS,limitation)
#Data_Person_1
```





```{r}
#Re-level the variables


#Salary

Data_Person_1$Salary_lvl<-with(Data_Person_1,ifelse(Salary =="1","0-$4999",ifelse(Salary=="2","$5000-$9999",ifelse(Salary=="3","$10000-$14999", ifelse(Salary=="4","$15000-$19999", ifelse(Salary =="5","$20000-$24999",ifelse(Salary=="6","$25000-$34999",ifelse(Salary=="7","$35000-$44999", ifelse(Salary =="8","$45000-$54999",ifelse(Salary=="9","$55000-$64999", ifelse(Salary =="10","$65000-$74999", ifelse(Salary=="11", "$75000 and over","Unknown"))))))))))))


# Limitation

Data_Person_1$Limitation_lvl<-with(Data_Person_1, ifelse(limitation =="0","2", "1"))


# Education

# Re-level and rename Education

Data_Person_1$Education_lvl<-with(Data_Person_1,ifelse(Education=="0"|Education=="1"|Education=="2"|Education=="3"|Education=="4"|Education=="5"|Education=="6"|Education=="7"|Education=="8"|Education=="9"|Education=="10"|Education=="11"|Education=="12"," Less than 12th grade, no high school diploma",ifelse(Education=="13"|Education=="14","GED recipient/High school graduate",ifelse(Education=="15","Some college, no degree", ifelse(Education=="16"|Education=="17","AA degree", ifelse(Education=="18","BA, BS, AB, BBA",ifelse(Education=="19"|Education=="20","Master's or doctoral",ifelse(Education == "21", "PhD", "Unknown"))))))))

```



```{r}
#Create a new variable Poverty_Guid

Data_Person_1$Poverty_Guid<-with(Data_Person_1, ifelse((Salary_lvl=="0-$4999"|Salary_lvl=="$5000-$9999"), "1","2"))
#Data_Person_1$Poverty_Guid
#table(Data_Person_1$Poverty_Guid)

```



```{r}
# Join Data_join_1 with Data_Person_1 and called it Data_join_2

#Data_join_2<-inner_join(Data_join_1,Data_Person_1 , by = c("HHX1" ="HHX2", "Family_no"="Family_no_1"))
#Data_join_2%>%select(HHX, Family_no,Person_no, everything())

```

##Data_Sample_Adult
### First rename the variables, then create a new data frame "Data_Sample_Adult_1". Join by HHX, Family_no, and Person_no the new data with Data_Person_1 to create "Data_join_4" then join it HHX and Family_no with "Data_join_1" to create "Data_join_4".

```{r}
#Rename Variables 

HHX3<-Data_Sample_Adult$HHX

Person_no_1<- Data_Sample_Adult$FPX

Family_no_2<-Data_Sample_Adult$FMX

Heart_Disease<-Data_Sample_Adult$HRTEV

Asthma<-Data_Sample_Adult$AASMEV

Cancer<-Data_Sample_Adult$CANEV

Diabetes<-Data_Sample_Adult$DIBEV

Sinusitis<-Data_Sample_Adult$SINYR

Chronic_Bronchitis<-Data_Sample_Adult$CBRCHYR

Failing_Kidney<-Data_Sample_Adult$KIDWKYR

Liver<-Data_Sample_Adult$LIVYR

Limited_Arthritis<-Data_Sample_Adult$ARTHLMT

Hearing_Aid<-Data_Sample_Adult$HEARAID

Vision<-Data_Sample_Adult$AVISION

Blind<-Data_Sample_Adult$ABLIND

Special_Equip<-Data_Sample_Adult$SPECEQ

Mental_Retardation<-Data_Sample_Adult$AFLHCA14

Developmental_Problem<-Data_Sample_Adult$AFLHCA15

Memory_Problem<-Data_Sample_Adult$AFLHCA16 

Emotional_Problem<-Data_Sample_Adult$AFLHCA17

Weight_Problem<-Data_Sample_Adult$AFLHCA18 

Missing_limb<-Data_Sample_Adult$AFLHC19_

Connective_tissue_prob<-Data_Sample_Adult$AFLHC20_

Circulation_problem<-Data_Sample_Adult$AFLHC21_

Bengin_Tumor<-Data_Sample_Adult$AFLHC22_

Nervous_System<-Data_Sample_Adult$AFLHC23_

Digestive_problem<-Data_Sample_Adult$AFLHC24_

Gen_problem<-Data_Sample_Adult$AFLHC25_

Skin_problem<-Data_Sample_Adult$AFLHC26_

Blood_problem<-Data_Sample_Adult$AFLHC27_

Parkinson<-Data_Sample_Adult$AFLHC28_

mental_illness<-Data_Sample_Adult$AFLHC30_

Surgical_after_effect<-Data_Sample_Adult$AFLHC31_

Old_age<-Data_Sample_Adult$AFLHC32_

Other_impairment<-Data_Sample_Adult$AFLHCA90

Functional_Limitation<-Data_Sample_Adult$FLA1AR

Alcohol<-Data_Sample_Adult$AFLHC29_

 

```



```{r}

# Create a new dataframe

Data_Sample_Adult_1<-data.frame(HHX3,Person_no_1,Family_no_2,Heart_Disease,Asthma,Cancer,Diabetes,Sinusitis,Chronic_Bronchitis,Failing_Kidney,Liver,Limited_Arthritis,Hearing_Aid,Vision,Blind,Special_Equip,Functional_Limitation,Mental_Retardation,Developmental_Problem,Memory_Problem,Emotional_Problem,Weight_Problem,Missing_limb,Connective_tissue_prob,Circulation_problem,Bengin_Tumor,Nervous_System,Digestive_problem,Gen_problem,Skin_problem,Blood_problem,Parkinson,mental_illness,Surgical_after_effect,Old_age,Other_impairment,Alcohol)
```



```{r}
# Join Data_Sample_Adult_1 and Data_Person_1 by HHX, Person_no, and Family_no as identifier
Data_join_4<-inner_join(Data_Sample_Adult_1,Data_Person_1 , by = c("HHX3" ="HHX2", "Family_no_2"="Family_no_1","Person_no_1"="Person_no"))
```



```{r}
# Join Data_join_4 and Data_join_1 by HHX and Family_no
Data_join_5<-inner_join(Data_join_4,Data_join_1, by=c("HHX3"="HHX1", "Family_no_2"="Family_no"))
```



```{r}

Data_join_filter<-Data_join_5%>%filter(!is.na(US_Citizen),!is.na(Receive_SSI),!is.na(Salary_lvl),!is.na(Functional_Limitation),!is.na(Other_impairment),Region=="2",Sample_Adult=="1")%>%mutate (Any_Disease = ifelse((Asthma=="1"|Cancer=="1"|Diabetes=="1"|Sinusitis=="1"| Chronic_Bronchitis=="1"| Failing_Kidney=="1"|Liver=="1"| Limited_Arthritis=="1"| Hearing_Aid=="1"|Vision=="1"| Blind=="1"| Mental_Retardation=="1"| Developmental_Problem=="1"|Memory_Problem=="1"|  Emotional_Problem=="1" |Weight_Problem=="1"|  Missing_limb=="1"| Connective_tissue_prob=="1"|  Circulation_problem=="1"| Bengin_Tumor=="1"| Nervous_System =="1"| Digestive_problem=="1"| Gen_problem=="1"|Skin_problem=="1"| Blood_problem=="1"| Parkinson=="1"| mental_illness=="1"|Surgical_after_effect=="1"| Old_age=="1"),"1",ifelse((Asthma=="2"|Cancer=="2"|Diabetes=="2"|Sinusitis=="2"| Chronic_Bronchitis=="2"| Failing_Kidney=="2"|Liver=="2"| Limited_Arthritis=="2"| Hearing_Aid=="2"|Vision=="2"| Blind=="2"|  Mental_Retardation=="2"|Developmental_Problem=="2"|Memory_Problem=="2"|  Emotional_Problem=="2"|Weight_Problem=="2"|  Missing_limb=="2"| Connective_tissue_prob=="2"|  Circulation_problem=="2"| Bengin_Tumor=="2"| Nervous_System =="2"| Digestive_problem=="2"| Gen_problem=="2"|Skin_problem=="2"| Blood_problem=="2"| Parkinson=="2"| mental_illness=="2"|Surgical_after_effect=="2"| Old_age=="2"), "2","3" )))#%>%select(Any_Disease,US_Citizen,Receive_SSI,Salary_lvl,Functional_Limitation)

```


```{r}
library(Hmisc)
table(Data_join_filter$Any_Disease, useNA = "always")

Data_join_filter$Any_disease_1 <- with(Data_join_filter, ifelse(is.na(Any_Disease),"2", "1"))
table(Data_join_filter$Any_disease_1)

```




```{r}
tbl_percent<-function(x){
  
  tbl<-table(x)
  res<-cbind(tbl, round(prop.table(tbl)*100,2))
  colnames(res)<-c('Count','Percentage')
  res
}

tbl_percent(Data_join_filter$Cancer)
```

```{r}
tbl_percent(Data_join_filter$Alcohol)

```




```{r}
tbl_percent(Data_join_filter$Asthma)

```


```{r}
tbl_percent(Data_join_filter$Bengin_Tumor)

```

```{r}
tbl_percent(Data_join_filter$Blind)

```

```{r}
tbl_percent(Data_join_filter$Blood_problem)

```

```{r}
tbl_percent(Data_join_filter$Chronic_Bronchitis)

```

```{r}
tbl_percent(Data_join_filter$Circulation_problem)

```

```{r}
tbl_percent(Data_join_filter$Connective_tissue_prob)

```

```{r}
tbl_percent(Data_join_filter$Developmental_Problem)

```

```{r}
tbl_percent(Data_join_filter$Diabetes)

```

```{r}
tbl_percent(Data_join_filter$Digestive_problem)

```

```{r}
tbl_percent(Data_join_filter$Emotional_Problem)

```

```{r}
tbl_percent(Data_join_filter$Failing_Kidney)

```

```{r}
tbl_percent(Data_join_filter$Gen_problem)

```

```{r}
tbl_percent(Data_join_filter$Hearing_Aid)

```

```{r}
tbl_percent(Data_join_filter$Heart_Disease)

```

```{r}
tbl_percent(Data_join_filter$Limited_Arthritis)

```

```{r}
tbl_percent(Data_join_filter$Liver)

```

```{r}
tbl_percent(Data_join_filter$Memory_Problem)

```

```{r}
tbl_percent(Data_join_filter$mental_illness)

```

```{r}
tbl_percent(Data_join_filter$Mental_Retardation)

```


```{r}
tbl_percent(Data_join_filter$Missing_limb)

```

```{r}
tbl_percent(Data_join_filter$Nervous_System)

```

```{r}
tbl_percent(Data_join_filter$Old_age)

```

```{r}
tbl_percent(Data_join_filter$Parkinson)

```

```{r}
tbl_percent(Data_join_filter$Sinusitis)

```

```{r}
tbl_percent(Data_join_filter$Skin_problem)

```

```{r}
tbl_percent(Data_join_filter$Surgical_after_effect)

```

```{r}
tbl_percent(Data_join_filter$Vision)

```

```{r}
tbl_percent(Data_join_filter$Weight_Problem)

```



```{r}

```




```{r}

```




```{r}

```



```{r}

```





```{r}

```



```{r}

```




```{r}

```



```{r}
ggplot(Data_join_filter)+geom_bar(aes(as.factor(Asthma), fill=as.factor(Receive_SSI)) )+labs(x="Asthma", y = "count", title="Distribution of Asthma")
```


```{r}
ggplot(Data_join_filter)+geom_bar(aes(as.factor(Any_Disease)))+labs(x="Asthma", y = "count", title="Distribution of Asthma")
```




```{r}
Data_join_4%>%filter( !is.na(Employed), Sample_Adult== "1")%>%ggplot()+geom_bar(aes(as.factor(Employed), fill = as.factor(Sex)))+labs(x="Employed", y = "count", title="Distribution of the Gender of Working Adult")
# 1 male, 2 femal
```

```{r}
Data_join_4%>%filter(!is.na(Salary_lvl))%>%ggplot()+geom_bar(aes(as.factor(Salary_lvl), fill=as.factor(Education_lvl)))+labs(x="Salary", y = "count", title="Distribution of Salary")+facet_wrap(~Employed)+coord_flip()
```

```{r}
Data_join_4%>%filter(!is.na(Limited_Arthritis), Limited_Arthritis=="1"|Limited_Arthritis=="2")%>%ggplot()+geom_bar(aes(as.factor(Limited_Arthritis), fill=as.factor(Limitation_lvl)))+labs(x="Arthritis", y = "count", title="Adult diagnosed with Arthritis, receive SSI, and have limitation")+facet_wrap(~Receive_SSI)
```



```{r}
Data_join_5%>%filter(US_Citizen == "1"|US_Citizen=="2", Receive_SSI=="1"|Receive_SSI=="2")%>%ggplot()+ geom_bar(aes(as.factor(US_Citizen),fill = as.factor(Functional_Limitation)))+labs(x="US_Citizen", title="US Citizens receiving SSI and Have Functional Limitation") + facet_wrap(~as.factor(Receive_SSI))
```

